mturk_data_processing

### 2018-01-21 experiments/3_processed_data/mturk_data_processing.Rmd
added the csv file. some participants had 25 responses

```{r}
# read the json file names to be loaded in the json directory
files <- dir("../1_raw_data/", pattern =".json") 
# make an empty data frame to append the json data participant by participant
adult_data <- data.frame()

#loop through json files
for (file in files) {
  #read the json file into jd
  jd <- fromJSON(paste(readLines(paste("../1_raw_data/", file, sep="")), collapse=""))
  #create a data frame with the column names on the left
  id <- data_frame(participant = jd$WorkerId,
                  gender = jd$answers$data$gen,
                  age = jd$answers$data$age,
                  Lang = jd$answers$data$language,
                  version = jd$answers$data$version,
                  logical_training = jd$answers$data$education,
                  trials = jd$answers$data$trial,
                  response = jd$answers$data$response,
                  duration = jd$answers$data$elapsed_ms,
                  AgeGroup = "adult",
                  aim = jd$answers$data$expt_aim,
                  comments = jd$answers$data$expt_gen
                  )
  # append the dataframe for that json file to the big data frame 
  adult_data <- bind_rows(adult_data, id)
}

write.csv(adult_data, "../2_processed_data/adult_data.csv")
```

>>>>

```{r}
# read the json file names to be loaded in the json directory
files <- dir("../2_raw_data/", pattern =".json") 
# make an empty data frame to append the json data participant by participant
adult_data <- data.frame()

#loop through json files
for (file in files) {
  #read the json file into jd
  jd <- fromJSON(paste(readLines(paste("../2_raw_data/", file, sep="")), collapse=""))
  #create a data frame with the column names on the left
  id <- data_frame(participant = jd$WorkerId,
                  gender = jd$answers$data$gen,
                  age = jd$answers$data$age,
                  language = jd$answers$data$language,
#                  version = jd$answers$data$version,
                  logical_training = jd$answers$data$education,
                  trials = jd$answers$data$trial,
                  response = jd$answers$data$response,
#                  duration = jd$answers$data$elapsed_ms,
#                  AgeGroup = "adult",
                  aim = jd$answers$data$expt_aim,
                  comments = jd$answers$data$expt_gen
                  )
  # append the dataframe for that json file to the big data frame 
  adult_data <- bind_rows(adult_data, id)
}

write.csv(adult_data, "../3_processed_data/adult_data.csv")
```
